\section*{First-author articles in international peer-reviewed journals}
\begin{itemize}
\item \bibentry{Bahl2023} 

This also forms the basis of patent application number 2309106.9 where the first author is listed as an inventor.

\item Anisha Bahl, Silvere Segaud, Yijing Xie, Jonathan Shapey, Mads Bergholt and Tom Vercauteren. \textit{A comparative study of analytical models of diffuse reflectance in homogeneous biological tissues: Gelatin based phantoms and monte carlo experiments.} Under review.

\item Anisha Bahl, Jonathan Shapey, Mads Bergholt and Tom Vercauteren. \textit{Evaluation of a two-layer skin tissue model for diffuse reflectance:
A simulated and experimental data study.} Under preparation.
% \item \bibentry{Bahl2023a}
% \input{PhD-Thesis-LOP_1.bib}
%Update when 1-layer published
%Add in 2-layer paper when preprint or published
\end{itemize}

\section*{First-author articles in international conferences with published proceedings}%Add tissue modelling reference via bibtex when proceedings published 
\begin{itemize}
\item Anisha Bahl, Silvere Segaud, Yijing Xie, Jonathan Shapey, Mads Bergholt and Tom Vercauteren. \textit{A comparative study of analytical tissue reflectance models
using simulated and experimental data.} Awaiting publication.
\end{itemize}

\section*{Co-author articles in international peer-reviewed journals}
\begin{itemize}
\item \bibentry{MacCormac2023}

\item \bibentry{Li2021}
\end{itemize}

\section*{Co-author pre-print articles}
\begin{itemize}
\item \bibentry{Xie2021}
\end{itemize}
